Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-15 paper/main.tex
fixing op
saving to clear out scraps

 \begin{definition} A presheaf \sheafc\, as introduced in \autoref{eq:related-work:continuity:presheaf}, is a functor $\sheaf: \mathcal{C}^{op} \rightarrow \textbf{Set}$.\cite{nlab:presheaf} \end{definition}

@@

As shown in \autoref{eq:artist:vindex}, the map between spaces $\vindex$ can be composed with section map $\dsection$ such that there is a map from the graphic base space $\gbase$ to the fiber bundle in which the data lives $\dtotal$.
\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{pullback.png}
  \label{fig:artist:pushforward_xi}
  \caption{The map $\vindex^*$ is a map from a repetition of the 1D fiber over every point $\dbasepoint \in \dbase$ in data space, turning the fiber into a 2D plane of repeating values over the corresponding region $\dbasepoint = \vindex(\gbasepoint)$ in the graphic space \gbase. }
\end{figure}
Since there is a mapping from the graphic space to the total bundle $\dsection \circ \vindex: \gbase \rightarrow \dtotal$, the mapping $\vindex$ can be pulled through the composition such that there is a map $\vindex^*$ between a total space over graphics $\vindex^*\dtotal$ and its equivalent space over data $\dtotal$.  As illustrated in the example given in \autoref{fig:artist:pushforward_xi}, a bundle $\dtotal$ over a point $\dbasepoint \in \dbase$ is pulled back through \vindex\ \cite{nlab:pullback_bundle} such that it is copied over every point in the corresponding region in graphic space $\vindex(\gbasepoint) = \dbasepoint, \gbasepoint \subset \gbase$. The pullback $\vindex^*$ can then be composed with the elements of the set of sections 
\begin{equation}
  \label{eq:artist:data_gamma_pullback}
 \cgamma{\dbasec}{\dtotalc} \textcolor{artist}{\xrightarrow{\vindex^*}} \cgamma{\gbasec}{\vindexc^*\dtotalc}
\end{equation}
to generate a set of equivalent sections over the graphic space $\Gamma(\gbase, \vindex^*{\dtotal})$. As a consequence of \autoref{eq:artist:data_gamma_pullback}, there exists a data sheaf over graphic space 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf_gamma}
\sheafc_{\vindexc^*}(\dtotalc): \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \cgamma{\gbasec}{\vindexc^*{\dtotalc}}
\end{equation}
which is equivalent to 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf}
  \sheafc_{\vindexc^*}(\dtotalc): \mathcal{\gbasec^{\textcolor{base}{op}}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}

>>>>

 \begin{definition} A presheaf \sheafc\, as introduced in \autoref{eq:related-work:continuity:presheaf}, is a functor $\sheaf: \mathcal{C}^{op} \rightarrow \textbf{Set}$.\cite{nlab:presheaf } \end{definition} \note{possibly add in from Hader lecture notes}

@@

As shown in \autoref{eq:artist:vindex}, the map between spaces $\vindex$ can be composed with section map $\dsection$ such that there is a map from the graphic base space $\gbase$ to the fiber bundle in which the data lives $\dtotal$.
\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{pullback.png}
  \label{fig:artist:pushforward_xi}
  \caption{The map $\vindex^*$ is a map from a repetition of the 1D fiber over every point $\dbasepoint \in \dbase$ in data space, turning the fiber into a 2D plane of repeating values over the corresponding region $\dbasepoint = \vindex(\gbasepoint)$ in the graphic space \gbase. }
\end{figure}
Since there is a mapping from the graphic space to the total bundle $\dsection \circ \vindex: \gbase \rightarrow \dtotal$, the mapping $\vindex$ can be pulled through the composition such that there is a map $\vindex^*$ between a total space over graphics $\vindex^*\dtotal$ and its equivalent space over data $\dtotal$.  As illustrated in the example given in \autoref{fig:artist:pushforward_xi}, a bundle $\dtotal$ over a point $\dbasepoint \in \dbase$ is pulled back through \vindex\ \cite{nlab:pullback_bundle} such that it is copied over every point in the corresponding region in graphic space $\vindex(\gbasepoint) = \dbasepoint, \gbasepoint \subset \gbase$. The pullback $\vindex^*$ can then be composed with the elements of the set of sections 
\begin{equation}
  \label{eq:artist:data_gamma_pullback}
 \cgamma{\dbasec}{\dtotalc} \textcolor{artist}{\xrightarrow{\vindex^*}} \cgamma{\gbasec}{\vindexc^*\dtotalc}
\end{equation}
to generate a set of equivalent sections over the graphic space $\Gamma(\gbase, \vindex^*{\dtotal})$. As a consequence of \autoref{eq:artist:data_gamma_pullback}, there exists a data sheaf over graphic space 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf_gamma}
\sheafc_{\vindexc^*}(\dtotalc): \mathcal{\gbasec}^{\textcolor{base}{op}} \textcolor{sheaf}{\rightarrow} \cgamma{\gbasec}{\vindexc^*{\dtotalc}}
\end{equation}
which is equivalent to 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf}
  \sheafc_{\vindexc^*}(\dtotalc): \mathcal{\gbasec}^{\textcolor{base}{op}} \textcolor{sheaf}{\rightarrow} \setc
\end{equation}
